### 2015-11-26 ch02-qlogms/excitation-design.tex
Some intro on Input design

@@

\subsection{Robust excitation signals}
\label{sec:excitation:intro:robust}
As illustrated above, optimal experiment design places the user in a catch-22 situation.
In the recent years, this has sparked attention towards robust signal design~\citep{Rojas2007} to alleviate the drawbacks of (nominal) optimal experiment design.
%TODO

@@

  The main problem is that network and dynamic signal analyzers typically
  rely on an equidistant frequency grid that comes with the Discrete Fourier Transform (DFT).
  A logarithmically spaced signal, on the other hand, does not match well to an equidistant frequency grid.
  More specifically, the lack of frequency resolution at the lowest frequencies hampers the quality of the power distribution at the low edge of the frequency band.
  To circumvent this disadvantage, we will construct quasi-logarithmically spaced signals.
  Their frequency spacing is approximately logarithmic but nevertheless conforms to the DFT's linear frequency grid.
  This problem was already discussed in \citet{Geerardyn2012IMTC}.

@@

  \begin{example}
   Consider the generalized multisine of the previous example to which a spectral component is added at $f_3 = \pi \unit{Hz}$, or equivalently one with a period of $T_3 = \pi^{-1} \unit{s}$.
   Then it is not possible to determine integer values $n_1$, $n_2$, $n_3$ such that $n_1 T_1 = n_2 T_2 = n_3 T_3$ since $T_3$ is an irrational number (unlike $T_1$ and $T_2$).
   Consequently, such a generalized `multisine' is not periodic.
  \end{example}

@@

>>>>

\begin{conjecture}
To identify the transfer function of a system, one has to apply an excitation signal to its input.
\end{conjecture}
\begin{conjecture}
To know which excitation signal is a good signal to excite the system with, one needs to know the system.
\end{conjecture}

The two conjectures above illustrate the catch-22 a practicing modeler finds himself in: if one wishes to identify a system, one needs to apply a signal; but to determine a good signal, one needs to know the system.
This conundrum becomes especially worrisome if one not only wants to use a `good' excitation signal, but rather the `best' excitation signal.

In this chapter, we will investigate how one can develop excitation signals that try to alleviate this paradox by imposing heuristic prior knowledge about the system that is more generic than in a typical (robust) optimal input design, but less wasteful than typical generic full multisine signals.

@@

\subsection{Robust excitation signals}
\label{sec:excitation:intro:robust}
As illustrated above, optimal experiment design places the user in a catch-22 situation\footnote{See the 1961 Joseph Heller novel `Catch-22'.}.
In the recent years, this has sparked attention towards robust signal design~\citep{Rojas2007} to alleviate the drawbacks of (nominal) optimal experiment design.
%TODO

@@

  The main problem is that network and dynamic signal analyzers typically
  rely on an equidistant frequency grid that comes with the Discrete Fourier Transform (DFT).
  A logarithmically spaced signal, on the other hand, does not match well to an equidistant frequency grid.
  More specifically, the lack of frequency resolution at the lowest frequencies hampers the quality of the power distribution at the low edge of the frequency band.
  To circumvent this disadvantage, we will construct quasi-logarithmically spaced signals.
  Their frequency spacing is approximately logarithmic but nevertheless conforms to the DFT's linear frequency grid.

@@

  \begin{example}
   Consider the generalized multisine of the previous example to which a spectral component is added at $f_3 = \pi \unit{Hz}$, or equivalently one with a period of $T_3 = \pi^{-1} \unit{s}$.
   Then it is not possible to determine integer values $n_1$, $n_2$, $n_3$ such that $n_1 T_1 = n_2 T_2 = n_3 T_3$ since $T_3$ is an irrational number of seconds (unlike $T_1$ and $T_2$).
   Consequently, such a generalized `multisine' is not periodic.
  \end{example}

@@

\TODO{cov-matrix uitschrijven}
